---
title: "Backlink Analysis"
output: 
  html_document:
    toc: true
    toc_float: true
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library(tidyverse)
library(readxl)
library(here)
library(knitr)
library(kableExtra)
```


```{r, echo=FALSE}
## ---- readdata
pdn <- readxl::read_xlsx(here("data-raw", 
                              "2022-08-17_07-19_new-explorer-backlinks_fresh_domain_pdn-ac-lk.xlsx"))

cmb <- readxl::read_xlsx(here("data-raw", 
                              "2022-08-17_07-20_new-explorer-backlinks_fresh_domain_cmb-ac-lk.xlsx"))
sjp <- readxl::read_xlsx(here("data-raw", 
                              "2022-08-17_07-20_new-explorer-backlinks_fresh_domain_sjp-ac-lk.xlsx"))

kdu <- readxl::read_xlsx(here("data-raw", 
                              "2022-08-17_07-21_new-explorer-backlinks_fresh_domain_kdu-ac-lk.xlsx"))


kln <- readxl::read_xlsx(here("data-raw", 
                              "2022-08-17_07-21_new-explorer-backlinks_fresh_domain_kln-ac-lk.xlsx"))

sliit <- readxl::read_xlsx(here("data-raw", 
                              "2022-08-17_07-21_new-explorer-backlinks_fresh_domain_sliit-lk.xlsx"))

```

# Target URLs

## Number of unique target urls

```{r, echo=FALSE}
sjpc <- length(unique(sjp$`Target URL`))
cmbc <- length(unique(cmb$`Target URL`))
kduc <- length(unique(kdu$`Target URL`))
klnc <- length(unique(kln$`Target URL`))
pdnc <- length(unique(pdn$`Target URL`))
sliitc <- length(unique(sliit$`Target URL`))

tu <- data.frame(University=c("SJP", "CMB", "KDU", "KLN", "PDN", "SLIIT"), Count = c(sjpc, cmbc, kduc, klnc, pdnc, sliitc))

ggplot(tu,aes(x= reorder(University,Count),Count))+geom_bar(stat ="identity") + coord_flip() + geom_text(aes(label = signif(Count)), nudge_y = 35) + xlab("University Code") +ylab("Count")
```

## Top 20 Target URLs

### University of Sri Jayewardenepura

```{r, echo=FALSE}
toptarget <- sjp %>%
  count(`Target URL`, sort=TRUE) %>% top_n(20)
toptarget %>% kable( "html", table.attr = "style='width:10%;'") %>%
  kableExtra::kable_styling(full_width = F)
```

### University of Colombo

```{r, echo=FALSE}
toptarget <- cmb %>%
  count(`Target URL`, sort=TRUE) %>% top_n(20)
toptarget %>% kable( "html", table.attr = "style='width:10%;'") %>%
  kableExtra::kable_styling(full_width = F)
```

### University of Peradeniya

```{r, echo=FALSE}
toptarget <- pdn %>%
  count(`Target URL`, sort=TRUE) %>% top_n(20)
toptarget %>% kable( "html", table.attr = "style='width:10%;'") %>%
  kableExtra::kable_styling(full_width = F)
```

### University of Kelaniya

```{r, echo=FALSE}
toptarget <- kln %>%
  count(`Target URL`, sort=TRUE) %>% top_n(20)
toptarget %>% kable( "html", table.attr = "style='width:10%;'") %>%
  kableExtra::kable_styling(full_width = F)
```

### SLIIT

```{r, echo=FALSE}
toptarget <- sliit %>%
  count(`Target URL`, sort=TRUE) %>% top_n(20)
toptarget %>% kable( "html", table.attr = "style='width:10%;'") %>%
  kableExtra::kable_styling(full_width = F)
```

### KDU

```{r, echo=FALSE}
toptarget <- kdu %>%
  count(`Target URL`, sort=TRUE) %>% top_n(20)
toptarget %>% kable( "html", table.attr = "style='width:10%;'") %>%
  kableExtra::kable_styling(full_width = F)
```

# Source link analysis/ Domains

## Number of unique source links/ domains

```{r, echo=FALSE}
sjps <- length(unique(sjp$`Source URL`))
cmbs <- length(unique(cmb$`Source URL`))
kdus <- length(unique(kdu$`Source URL`))
klns <- length(unique(kln$`Source URL`))
pdns <- length(unique(pdn$`Source URL`))
sliits <- length(unique(sliit$`Source URL`))

su <- data.frame(University=c("SJP", "CMB", "KDU", "KLN", "PDN", "SLIIT"), Count = c(sjps, cmbs, kdus, klns, pdns, sliits))

ggplot(su,aes(x= reorder(University,Count),Count))+geom_bar(stat ="identity") + coord_flip() + geom_text(aes(label = signif(Count)), nudge_y = 50) + xlab("University Code") +ylab("Count")
```


# Source Topical Trust Flow

University of Sri Jayewardenepura

```{r, echo=FALSE}
trustsjp <- sjp %>%
  count(`Source Topical Trust Flow Topic 0`, sort=TRUE) %>% top_n(10)
trustsjp %>% kable( "html", table.attr = "style='width:10%;'") %>%
  kableExtra::kable_styling(full_width = F)
```

University of Colombo

```{r, echo=FALSE}
trustcmb <- cmb %>%
  count(`Source Topical Trust Flow Topic 0`, sort=TRUE) %>% top_n(10)
trustcmb %>% kable( "html", table.attr = "style='width:10%;'") %>%
  kableExtra::kable_styling(full_width = F)
```

University of Kelaniya

```{r, echo=FALSE}
trustkln <- kln %>%
  count(`Source Topical Trust Flow Topic 0`, sort=TRUE) %>% top_n(10)
trustkln %>% kable( "html", table.attr = "style='width:10%;'") %>%
  kableExtra::kable_styling(full_width = F)
```

KDU


```{r, echo=FALSE}
trustkdu <- kdu %>%
  count(`Source Topical Trust Flow Topic 0`, sort=TRUE) %>% top_n(10)
trustkdu %>% kable( "html", table.attr = "style='width:10%;'") %>%
  kableExtra::kable_styling(full_width = F)
```

SLIIT

```{r, echo=FALSE}
trustsliit <- sliit %>%
  count(`Source Topical Trust Flow Topic 0`, sort=TRUE) %>% top_n(10)
trustsliit %>% kable( "html", table.attr = "style='width:10%;'") %>%
  kableExtra::kable_styling(full_width = F)
```




