---
title: "Backlink Analysis"
output: 
  flexdashboard::flex_dashboard:
    theme:
      bg: "#FFFFFF"
      fg: "#000437" 
      primary: "#9e0b37"
      base_font:
        google: Prompt
      code_font:
        google: JetBrains Mono
    orientation: columns
    vertical_layout: fill
---

```{r setup, include=FALSE}
library(flexdashboard)
# Install thematic and un-comment for themed static plots (i.e., ggplot2)
# thematic::thematic_rmd()
```

```{r, include=FALSE}
library(tidyverse)
library(readxl)
library(here)
library(knitr)
library(kableExtra)
library(plotly)
library(patchwork)
library(ggridges)
```


```{r, echo=FALSE}
## ---- readdata
pdn <- readxl::read_xlsx(here("data-raw", 
                              "2022-08-17_07-19_new-explorer-backlinks_fresh_domain_pdn-ac-lk.xlsx"))

cmb <- readxl::read_xlsx(here("data-raw", 
                              "2022-08-17_07-20_new-explorer-backlinks_fresh_domain_cmb-ac-lk.xlsx"))
sjp <- readxl::read_xlsx(here("data-raw", 
                              "2022-08-17_07-20_new-explorer-backlinks_fresh_domain_sjp-ac-lk.xlsx"))

kdu <- readxl::read_xlsx(here("data-raw", 
                              "2022-08-17_07-21_new-explorer-backlinks_fresh_domain_kdu-ac-lk.xlsx"))


kln <- readxl::read_xlsx(here("data-raw", 
                              "2022-08-17_07-21_new-explorer-backlinks_fresh_domain_kln-ac-lk.xlsx"))

sliit <- readxl::read_xlsx(here("data-raw", 
                              "2022-08-17_07-21_new-explorer-backlinks_fresh_domain_sliit-lk.xlsx"))

```

# Overview

Column {data-width=650}
-----------------------------------------------------------------------

### Total number of unique target links


```{r, echo=FALSE}
sjpc <- length(unique(sjp$`Target URL`))
cmbc <- length(unique(cmb$`Target URL`))
kduc <- length(unique(kdu$`Target URL`))
klnc <- length(unique(kln$`Target URL`))
pdnc <- length(unique(pdn$`Target URL`))
sliitc <- length(unique(sliit$`Target URL`))

tu <- data.frame(University=c("SJP", "CMB", "KDU", "KLN", "PDN", "SLIIT"), Count = c(sjpc, cmbc, kduc, klnc, pdnc, sliitc))

p1 <- ggplot(tu,aes(x= reorder(University,Count),Count))+geom_bar(stat ="identity") + coord_flip() + geom_text(aes(label = signif(Count)), nudge_y = 35) + xlab("University Code") +ylab("Count") 
p1
```


Column {data-width=650}
-----------------------------------------------------------------------

### Number of unique source links/ domains

```{r, echo=FALSE}
sjps <- length(unique(sjp$`Source URL`))
cmbs <- length(unique(cmb$`Source URL`))
kdus <- length(unique(kdu$`Source URL`))
klns <- length(unique(kln$`Source URL`))
pdns <- length(unique(pdn$`Source URL`))
sliits <- length(unique(sliit$`Source URL`))

su <- data.frame(University=c("SJP", "CMB", "KDU", "KLN", "PDN", "SLIIT"), Count = c(sjps, cmbs, kdus, klns, pdns, sliits))

p2 <- ggplot(su,aes(x= reorder(University,Count),Count))+geom_bar(stat ="identity") + coord_flip() + geom_text(aes(label = signif(Count)), nudge_y = 50) + xlab("University Code") +ylab("Count")
p2
```

# Source Link (Trust and Ciations Flow)


```{r}
sjp1 <- ggplot(sjp, aes(x=`Source Trust Flow`, y=`Source Citation Flow`)) +geom_point(alpha=0.5) + ggtitle("SJP - 0.53") 
cmb1 <- ggplot(cmb, aes(x=`Source Trust Flow`, y=`Source Citation Flow`)) +geom_point(alpha=0.5) + ggtitle("CMB - 0.51")
pdn1 <- ggplot(pdn, aes(x=`Source Trust Flow`, y=`Source Citation Flow`)) +geom_point(alpha=0.5) + ggtitle("PDN - 0.64")
kln1 <- ggplot(kln, aes(x=`Source Trust Flow`, y=`Source Citation Flow`)) +geom_point(alpha=0.5) + ggtitle("KLN - 0.64")
sliit1 <- ggplot(sliit, aes(x=`Source Trust Flow`, y=`Source Citation Flow`)) +geom_point(alpha=0.5) + ggtitle("SLIIT - 0.63")
kdu1 <- ggplot(kdu, aes(x=`Source Trust Flow`, y=`Source Citation Flow`)) +geom_point(alpha=0.5) + ggtitle("KDU - 0.61")
(sjp1+cmb1+pdn1)/(kln1+sliit1+kdu1)
```



```{r, eval=FALSE}
sjp %>% select(c(`Source Trust Flow`, `Source Citation Flow`)) %>% summarize(SJP = cor(`Source Trust Flow`, `Source Citation Flow`)) %>% kable()

cmb %>% select(c(`Source Trust Flow`, `Source Citation Flow`)) %>% summarize(CMB = cor(`Source Trust Flow`, `Source Citation Flow`)) %>% kable()

pdn %>% select(c(`Source Trust Flow`, `Source Citation Flow`)) %>% summarize(PDN = cor(`Source Trust Flow`, `Source Citation Flow`)) %>% kable()

kln %>% select(c(`Source Trust Flow`, `Source Citation Flow`)) %>% summarize(KLN = cor(`Source Trust Flow`, `Source Citation Flow`)) %>% kable()

sliit %>% select(c(`Source Trust Flow`, `Source Citation Flow`)) %>% summarize(SLIIT = cor(`Source Trust Flow`, `Source Citation Flow`)) %>% kable()

kdu %>% select(c(`Source Trust Flow`, `Source Citation Flow`)) %>% summarize(KDU = cor(`Source Trust Flow`, `Source Citation Flow`)) %>% kable()







```

# Target (Trust and Ciations Flow)


```{r}
sjp3 <- ggplot(sjp, aes(x=`Target Trust Flow`, y=`Target Citation Flow`)) +geom_point(alpha=0.5) + ggtitle("SJP") 
cmb3 <- ggplot(cmb, aes(x=`Target Trust Flow`, y=`Target Citation Flow`)) +geom_point(alpha=0.5) + ggtitle("CMB")
pdn3 <- ggplot(pdn, aes(x=`Target Trust Flow`, y=`Target Citation Flow`)) +geom_point(alpha=0.5) + ggtitle("PDN")
kln3 <- ggplot(kln, aes(x=`Target Trust Flow`, y=`Target Citation Flow`)) +geom_point(alpha=0.5) + ggtitle("KLN")
sliit3 <- ggplot(sliit, aes(x=`Target Trust Flow`, y=`Target Citation Flow`)) +geom_point(alpha=0.5) + ggtitle("SLIIT")
kdu3 <- ggplot(kdu, aes(x=`Target Trust Flow`, y=`Target Citation Flow`)) +geom_point(alpha=0.5) + ggtitle("KDU")
(sjp3+cmb3+pdn3)/(kln3+sliit3+kdu3)
```

#### Correlation coefficient

```{r}
sjp %>% select(c(`Target Trust Flow`, `Target Citation Flow`)) %>% summarize(SJP = cor(`Target Trust Flow`, `Target Citation Flow`)) %>% kable()

cmb %>% select(c(`Target Trust Flow`, `Target Citation Flow`)) %>% summarize(CMB = cor(`Target Trust Flow`, `Target Citation Flow`)) %>% kable()

pdn %>% select(c(`Target Trust Flow`, `Target Citation Flow`)) %>% summarize(PDN = cor(`Target Trust Flow`, `Target Citation Flow`)) %>% kable()

kln %>% select(c(`Target Trust Flow`, `Target Citation Flow`)) %>% summarize(KLN = cor(`Target Trust Flow`, `Target Citation Flow`)) %>% kable()

sliit %>% select(c(`Target Trust Flow`, `Target Citation Flow`)) %>% summarize(SLIIT = cor(`Target Trust Flow`, `Target Citation Flow`)) %>% kable()

kdu %>% select(c(`Target Trust Flow`, `Target Citation Flow`)) %>% summarize(KDU = cor(`Target Trust Flow`, `Target Citation Flow`)) %>% kable()


```

# Domain (Trust and Ciations Flow)


```{r}
sjp2 <- ggplot(sjp, aes(x=`Domain Trust Flow`, y=`Domain Citation Flow`)) +geom_point(alpha=0.5) + ggtitle("SJP") 
cmb2 <- ggplot(cmb, aes(x=`Domain Trust Flow`, y=`Domain Citation Flow`)) +geom_point(alpha=0.5) + ggtitle("CMB")
pdn2 <- ggplot(pdn, aes(x=`Domain Trust Flow`, y=`Domain Citation Flow`)) +geom_point(alpha=0.5) + ggtitle("PDN")
kln2 <- ggplot(kln, aes(x=`Domain Trust Flow`, y=`Domain Citation Flow`)) +geom_point(alpha=0.5) + ggtitle("KLN")
sliit2 <- ggplot(sliit, aes(x=`Domain Trust Flow`, y=`Domain Citation Flow`)) +geom_point(alpha=0.5) + ggtitle("SLIIT")
kdu2 <- ggplot(kdu, aes(x=`Domain Trust Flow`, y=`Domain Citation Flow`)) +geom_point(alpha=0.5) + ggtitle("KDU")
(sjp2+cmb2+pdn2)/(kln2+sliit2+kdu2)
```

#### Correlation coefficient

```{r}
sjp %>% select(c(`Domain Trust Flow`, `Domain Citation Flow`)) %>% summarize(SJP = cor(`Domain Trust Flow`, `Domain Citation Flow`)) %>% kable()

cmb %>% select(c(`Domain Trust Flow`, `Domain Citation Flow`)) %>% summarize(CMB = cor(`Domain Trust Flow`, `Domain Citation Flow`)) %>% kable()

pdn %>% select(c(`Domain Trust Flow`, `Domain Citation Flow`)) %>% summarize(PDN = cor(`Domain Trust Flow`, `Domain Citation Flow`)) %>% kable()

kln %>% select(c(`Domain Trust Flow`, `Domain Citation Flow`)) %>% summarize(KLN = cor(`Domain Trust Flow`, `Domain Citation Flow`)) %>% kable()

sliit %>% select(c(`Domain Trust Flow`, `Domain Citation Flow`)) %>% summarize(SLIIT = cor(`Domain Trust Flow`, `Domain Citation Flow`)) %>% kable()

kdu %>% select(c(`Domain Trust Flow`, `Domain Citation Flow`)) %>% summarize(KDU = cor(`Domain Trust Flow`, `Domain Citation Flow`)) %>% kable()


```


# Summary statistics

Column {data-width=650 .tabset}
-----------------------------------------------------------------------

#### Summary statistics: source trust flow

```{r}
SJP <- sjp %>% select(c(`Source Trust Flow`, `Source Citation Flow`))
SJP <- SJP %>% pivot_longer(1:2, "type", "value")

PDN <- pdn %>% select(c(`Source Trust Flow`, `Source Citation Flow`))
PDN <- PDN %>% pivot_longer(1:2, "type", "value")

CMB <- cmb %>% select(c(`Source Trust Flow`, `Source Citation Flow`))
CMB <- CMB %>% pivot_longer(1:2, "type", "value")

KLN <- kln %>% select(c(`Source Trust Flow`, `Source Citation Flow`))
KLN <- KLN %>% pivot_longer(1:2, "type", "value")

SLIIT <- sliit %>% select(c(`Source Trust Flow`, `Source Citation Flow`))
SLIIT <- SLIIT %>% pivot_longer(1:2, "type", "value")

KDU <- kdu %>% select(c(`Source Trust Flow`, `Source Citation Flow`))
KDU <- KDU %>% pivot_longer(1:2, "type", "value")

institution <- c(rep("SJP" , dim(SJP)[1]), 
                 rep("PDN" , dim(PDN)[1]),
                 rep("CMB" , dim(CMB)[1]),
                 rep("KLN" , dim(KLN)[1]),
                 rep("SLIIT" , dim(SLIIT)[1]),
                 rep("KDU" , dim(KDU)[1]))

all <- bind_rows(SJP, PDN, CMB, KLN, SLIIT, KDU)
all$institution <- institution

all %>% filter(type=="Source Trust Flow") %>% group_by(institution) %>%
  summarise(mean = mean(value), median = median(value), sd = sd(value), maximum = max(value), n=n()) %>% arrange(desc(n)) %>%  kbl(align = "l") %>% 
    kable_styling()
  


```


#### Summary statistics: source citation flow

```{r}
all %>% filter(type=="Source Citation Flow") %>% group_by(institution) %>%
  summarise(mean = mean(value), median = median(value), sd = sd(value), maximum = max(value), n=n()) %>% arrange(desc(n)) %>%  kbl(align = "l") %>% 
    kable_styling()
```

Column {data-width=650 .tabset}
-----------------------------------------------------------------------

#### Summary statistics: domain trust flow

```{r}
SJP <- sjp %>% select(c(`Domain Trust Flow`, `Domain Citation Flow`))
SJP <- SJP %>% pivot_longer(1:2, "type", "value")

PDN <- pdn %>% select(c(`Domain Trust Flow`, `Domain Citation Flow`))
PDN <- PDN %>% pivot_longer(1:2, "type", "value")

CMB <- cmb %>% select(c(`Domain Trust Flow`, `Domain Citation Flow`))
CMB <- CMB %>% pivot_longer(1:2, "type", "value")

KLN <- kln %>% select(c(`Domain Trust Flow`, `Domain Citation Flow`))
KLN <- KLN %>% pivot_longer(1:2, "type", "value")

SLIIT <- sliit %>% select(c(`Domain Trust Flow`, `Domain Citation Flow`))
SLIIT <- SLIIT %>% pivot_longer(1:2, "type", "value")

KDU <- kdu %>% select(c(`Domain Trust Flow`, `Domain Citation Flow`))
KDU <- KDU %>% pivot_longer(1:2, "type", "value")

institution <- c(rep("SJP" , dim(SJP)[1]), 
                 rep("PDN" , dim(PDN)[1]),
                 rep("CMB" , dim(CMB)[1]),
                 rep("KLN" , dim(KLN)[1]),
                 rep("SLIIT" , dim(SLIIT)[1]),
                 rep("KDU" , dim(KDU)[1]))

all <- bind_rows(SJP, PDN, CMB, KLN, SLIIT, KDU)
all$institution <- institution

all %>% filter(type=="Domain Trust Flow") %>% group_by(institution) %>%
  summarise(mean = mean(value), median = median(value), sd = sd(value), maximum = max(value), n=n()) %>% arrange(desc(n)) %>%  kbl(align = "l") %>% 
    kable_styling()
  


```


#### Summary statistics: domain citation flow

```{r}
all %>% filter(type=="Domain Citation Flow") %>% group_by(institution) %>%
  summarise(mean = mean(value), median = median(value), sd = sd(value), maximum = max(value), n=n()) %>% arrange(desc(n)) %>%  kbl(align = "l") %>% 
    kable_styling()
```


Column {data-width=650 .tabset}
-----------------------------------------------------------------------

#### Summary statistics: target trust flow

```{r}
SJP <- sjp %>% select(c(`Target Trust Flow`, `Target Citation Flow`))
SJP <- SJP %>% pivot_longer(1:2, "type", "value")

PDN <- pdn %>% select(c(`Target Trust Flow`, `Target Citation Flow`))
PDN <- PDN %>% pivot_longer(1:2, "type", "value")

CMB <- cmb %>% select(c(`Target Trust Flow`, `Target Citation Flow`))
CMB <- CMB %>% pivot_longer(1:2, "type", "value")

KLN <- kln %>% select(c(`Target Trust Flow`, `Target Citation Flow`))
KLN <- KLN %>% pivot_longer(1:2, "type", "value")

SLIIT <- sliit %>% select(c(`Target Trust Flow`, `Target Citation Flow`))
SLIIT <- SLIIT %>% pivot_longer(1:2, "type", "value")

KDU <- kdu %>% select(c(`Target Trust Flow`, `Target Citation Flow`))
KDU <- KDU %>% pivot_longer(1:2, "type", "value")

institution <- c(rep("SJP" , dim(SJP)[1]), 
                 rep("PDN" , dim(PDN)[1]),
                 rep("CMB" , dim(CMB)[1]),
                 rep("KLN" , dim(KLN)[1]),
                 rep("SLIIT" , dim(SLIIT)[1]),
                 rep("KDU" , dim(KDU)[1]))

all <- bind_rows(SJP, PDN, CMB, KLN, SLIIT, KDU)
all$institution <- institution

all %>% filter(type=="Target Trust Flow") %>% group_by(institution) %>%
  summarise(mean = mean(value), median = median(value), sd = sd(value), maximum = max(value), n=n()) %>% arrange(desc(n)) %>%  kbl(align = "l") %>% 
    kable_styling()
  


```


#### Summary statistics: target citation flow

```{r}
all %>% filter(type=="Target Citation Flow") %>% group_by(institution) %>%
  summarise(mean = mean(value), median = median(value), sd = sd(value), maximum = max(value), n=n()) %>% arrange(desc(n)) %>%  kbl(align = "l") %>% 
    kable_styling()
```



# Top target URL

Column {data-width=650 .tabset}
-----------------------------------------------------------------------

### SJP

```{r}
toptarget <- sjp %>%
  count(`Target URL`, sort=TRUE) %>% top_n(20)
toptarget %>% kable( "html", table.attr = "style='width:10%;'") %>%
  kableExtra::kable_styling(full_width = F)
```

### CMB

```{r, echo=FALSE}
toptarget <- cmb %>%
  count(`Target URL`, sort=TRUE) %>% top_n(20)
toptarget %>% kable( "html", table.attr = "style='width:10%;'") %>%
  kableExtra::kable_styling(full_width = F)
```

### PDN

```{r, echo=FALSE}
toptarget <- pdn %>%
  count(`Target URL`, sort=TRUE) %>% top_n(20)
toptarget %>% kable( "html", table.attr = "style='width:10%;'") %>%
  kableExtra::kable_styling(full_width = F)
```

### KLN

```{r, echo=FALSE}
toptarget <- kln %>%
  count(`Target URL`, sort=TRUE) %>% top_n(20)
toptarget %>% kable( "html", table.attr = "style='width:10%;'") %>%
  kableExtra::kable_styling(full_width = F)
```

### SLIIT

```{r, echo=FALSE}
toptarget <- sliit %>%
  count(`Target URL`, sort=TRUE) %>% top_n(20)
toptarget %>% kable( "html", table.attr = "style='width:10%;'") %>%
  kableExtra::kable_styling(full_width = F)
```

### KDU

```{r, echo=FALSE}
toptarget <- kdu %>%
  count(`Target URL`, sort=TRUE) %>% top_n(20)
toptarget %>% kable( "html", table.attr = "style='width:10%;'") %>%
  kableExtra::kable_styling(full_width = F)
```




# Top 5 Source Topical Trust Flow Topic 0

Column {data-width=650}
-----------------------------------------------------------------------

#### SJP

```{r}
st <- sjp %>%
  count(`Source Topical Trust Flow Topic 0`, sort=TRUE) %>% top_n(5)
st %>% kable( "html", table.attr = "style='width:10%;'") %>%
  kableExtra::kable_styling(full_width = F)
```

#### CMB

```{r, echo=FALSE}
toptarget <- cmb %>%
  count(`Source Topical Trust Flow Topic 0`, sort=TRUE) %>% top_n(5)
toptarget %>% kable( "html", table.attr = "style='width:10%;'") %>%
  kableExtra::kable_styling(full_width = F)
```

Column {data-width=650}
-----------------------------------------------------------------------

#### PDN

```{r, echo=FALSE}
toptarget <- pdn %>%
  count(`Source Topical Trust Flow Topic 0`, sort=TRUE) %>% top_n(5)
toptarget %>% kable( "html", table.attr = "style='width:10%;'") %>%
  kableExtra::kable_styling(full_width = F)
```

#### KLN

```{r, echo=FALSE}
toptarget <- kln %>%
  count(`Source Topical Trust Flow Topic 0`, sort=TRUE) %>% top_n(5)
toptarget %>% kable( "html", table.attr = "style='width:10%;'") %>%
  kableExtra::kable_styling(full_width = F)
```

Column {data-width=650}
-----------------------------------------------------------------------

#### SLIIT

```{r, echo=FALSE}
toptarget <- sliit %>%
  count(`Source Topical Trust Flow Topic 0`, sort=TRUE) %>% top_n(5)
toptarget %>% kable( "html", table.attr = "style='width:10%;'") %>%
  kableExtra::kable_styling(full_width = F)
```

#### KDU

```{r, echo=FALSE}
toptarget <- kdu %>%
  count(`Source Topical Trust Flow Topic 0`, sort=TRUE) %>% top_n(5)
toptarget %>% kable( "html", table.attr = "style='width:10%;'") %>%
  kableExtra::kable_styling(full_width = F)
```

# Top 5 Source Topical Trust Flow Topic 1

Column {data-width=650}
-----------------------------------------------------------------------

#### SJP

```{r}
st <- sjp %>%
  count(`Source Topical Trust Flow Topic 1`, sort=TRUE) %>% top_n(5)
st %>% kable( "html", table.attr = "style='width:10%;'") %>%
  kableExtra::kable_styling(full_width = F)
```

#### CMB

```{r, echo=FALSE}
toptarget <- cmb %>%
  count(`Source Topical Trust Flow Topic 1`, sort=TRUE) %>% top_n(5)
toptarget %>% kable( "html", table.attr = "style='width:10%;'") %>%
  kableExtra::kable_styling(full_width = F)
```

Column {data-width=650}
-----------------------------------------------------------------------

#### PDN

```{r, echo=FALSE}
toptarget <- pdn %>%
  count(`Source Topical Trust Flow Topic 1`, sort=TRUE) %>% top_n(5)
toptarget %>% kable( "html", table.attr = "style='width:10%;'") %>%
  kableExtra::kable_styling(full_width = F)
```

#### KLN

```{r, echo=FALSE}
toptarget <- kln %>%
  count(`Source Topical Trust Flow Topic 1`, sort=TRUE) %>% top_n(5)
toptarget %>% kable( "html", table.attr = "style='width:10%;'") %>%
  kableExtra::kable_styling(full_width = F)
```

Column {data-width=650}
-----------------------------------------------------------------------

#### SLIIT

```{r, echo=FALSE}
toptarget <- sliit %>%
  count(`Source Topical Trust Flow Topic 1`, sort=TRUE) %>% top_n(5)
toptarget %>% kable( "html", table.attr = "style='width:10%;'") %>%
  kableExtra::kable_styling(full_width = F)
```

#### KDU

```{r, echo=FALSE}
toptarget <- kdu %>%
  count(`Source Topical Trust Flow Topic 1`, sort=TRUE) %>% top_n(5)
toptarget %>% kable( "html", table.attr = "style='width:10%;'") %>%
  kableExtra::kable_styling(full_width = F)
```




